Automatic Singing Transcription

### 2023-12-01 report/paper.tex
add to wav2vec 2

\documentclass[12pt]{article}
\usepackage[legalpaper, portrait, margin=1in]{geometry}
\usepackage{multicol}
\usepackage[english]{babel}
\usepackage{graphicx}

@@

\section{Related Works}
\subsection{Early HMM-Based Acoustic Models}

\subsection{Music Informed Models}
\subsection{wav2vec 2.0 and Transfer Learning} \label{sec:wav2vec}
\subsection{Whisper Word-Level Alignment}

@@

\section{Future Work}
\subsection{Adversarial Training}

@@

% \section*{Scholarly Articles}
% \begin{enumerate}
%     \item \cite{wav2vecTransfer}
%     \item \cite{wav2vec}
%     \item \cite{Librispeech}
%     \item \cite{whisper}
%     \item \cite{LyricAlignAcoustic}
%     \item \cite{Audio2Score}
%     \item \cite{PhonemeInformed}
%     \item \cite{Hansen}
%     \item \cite{KaraokeApp}
%     \item \cite{BayesianAST}
%     \item \cite{whisperX}
%     \item \cite{CSD}
%     \item \cite{DALI}
%     \item \cite{NUSDataset}
%     \item \cite{JamendoLyrics}
%     \item \cite{musDB18}
%     \item \cite{Demux}
%     \item \cite{CMUDict}
%     \item \cite{SpecAugment}
%     \item \cite{PhonationMode}
% \end{enumerate}
% \section*{Other Sources}
% \begin{enumerate}
%     \item \cite{MFCC}
%     \item \cite{CTC}
% \end{enumerate}
\bibliographystyle{apalike}
\bibliography{references}
\end{multicols*}
\end{document}

>>>>

\documentclass[letterpaper, 12pt]{article}
\usepackage[letterpaper, portrait, margin=1in]{geometry}
\usepackage{multicol}
\usepackage[english]{babel}
\usepackage{graphicx}

@@

\section{Related Works}
\subsection{HMM Based Acoustic Models}
The traditional approach to AST is can be separated into a pipeline of distinct steps. The first
step is to extract the features from the audio. This usually includes some form of spectral analysis
such as MFCCs. The second step is to use an acoustic model to classify the features into phonemes
and generate a sequence of phonemes using a Hidden Markov Model (HMM). This is the traditional
approach to ASR and is also used in AST \cite{Hansen}.

{
\color{red}
TODO: Add more detail about HMMs
TODO: Write about Dynamic Time Warping
TODO: Write about some results of HMMs
}

% \subsection{Music Informed Models}

\subsection{wav2vec 2.0 and Transfer Learning} \label{sec:wav2vec}

\subsubsection{wav2vec 2.0}
One of the most recent breakthroughs in ASR is wav2vec 2.0 \cite{wav2vec}. This model uses a
self-supervised learning approach was used during the training of the model. Unlabeled audio was
fed into the model to learn discrete speech units. These discrete speech units required the
Gumbel-Softmax \cite{gumbelSoftmax} to allow for backpropagation. The model was then
fine-tuned with a linear layer and CTC loss on labeled data to perform ASR \cite{wav2vec}.

This approach was able to achieve state-of-the-art results on the LibriSpeech dataset \cite{Librispeech}
and the TIMIT dataset \cite{TIMIT}. However, the thing that makes this approach the most promising
is the fact that after pre-training on a large amount of unlabeled data, the model can be fine-tuned
on a 10 minute subset of labeled data to achieve 5.2 WER on the LibriSpeech clean dataset \cite{wav2vec}.
This is very important for AST because there are so few labeled datasets available.

\subsubsection{wav2vec 2.0 Transfer Learning}
Using transfer learning for AST using wav2vec 2.0 was attempted in 2022 and was used to achieve
state-of-the-art results on the Jamendo dataset as well as on the DALI, Hansen, Mauch,
and DAMP! datasets \cite{wav2vecTransfer}. The approach they performed did not change the first part
of the model that generated the discrete speech units. Instead, they changed the last part of the
model to have another branch that outputs the probability of the current word given previous words
and context. This approach achieved a 33.13 WER on the Jamendo dataset \cite{wav2vecTransfer}.

Apart from their results, there were also a few other interesting things about their approach. Since
the initial wav2vec 2.0 model was trained on the LibriSpeech dataset, they wanted to make the input
audio of their model as similar to the LibriSpeech dataset as possible. To do this, they used
Demucs v3 \cite{Demux} to separate the vocals from the accompaniment. They did not futher remove any
noise or singing specific features from the audio. For their labeled datasets, they used
utterance level labels excluding the instrumental parts. For the output, they used character level
labels.

\subsection{Whisper Word-Level Alignment}

@@

\section{Future Work}
\subsection{Adversarial Training}
\subsection{Transform Singing to Speech Data}
remove pitch from singing

@@

\bibliographystyle{apalike}
\bibliography{references}
\end{multicols*}
\end{document}
